Vulnerability Analysis of Container Images in Neuroimaging

### 2020-03-03 paper.tex
updated materials and methods

In this section, we present our study methodology.
This study involves three image scanning experiments.
First experiment involves scanning
the images. For that purpose, we use three different scanners. Second experiment involves updating
all these images and then rescanning them. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.

We first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. Later, we discuss 
various Linux distributions and their releases. Lastly, this section
provides a description of the three scanning tools used.

@@

Tools that are capable of packing and running an application in an isolated environment
are known as container tools. Alongwith an application, they also pack the application's dependencies,
required libraries and configuration files for the
application to function properly. The functioning of an application in an isolated environment
is called a container. Containers directly run on the Host machine's kernel so they are lightweight.
Consequently, more containers can be run on a given Host machine as compared to virtual machines.

@@

Docker is a tool to run containers.
Docker containers are managed by the Docker engine, which is a client-server application and
consists of the following three main components:

@@

\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.

%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
If a user gets root privileges, it
introduces unthinkable security risks for multi-tenant shared
environments. Due to this reason, Docker is not supported by
HPC environments.

@@

\begin{comment}
Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.
\end{comment}

@@

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. 
\begin{comment}
DockerHub uses gzip compression for
transferring layers.There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch.Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}
\end{comment}

@@

On the other hand, a Singularity image is a single immutable file and 
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.
\begin{comment}
Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.
\end{comment}
\subsection{Application frameworks}

@@

\subsection{Linux Distributions}

@@

>>>>

This study involves three image scanning experiments.
The first experiment scans the images as is to report the existing vulnerabilities
inside the images. The scan report of
these images shows a large number of existing vulnerabilities which may pose
a potential security risk. These vulnerabilities exist due to the outdated
packages that are present inside images. So, the next step is to
take the necessary steps to improve security in the images. Therefore, there exist
two possible solutions.
The first one involves updating
all these images and then rescanning them, which constitutes the next experiment of our study. The second one
involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image, which will be presented as our third experiment.

We first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. 
Later, this section
presents two scanning techniques followed by a description of image scanners used.
In this study, we used three different image scanners because they
use different scanning techniques and/or refer to different vulnerability sources.
The images used in our study have different Linux distributions/releases, which have
different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.

@@

Container tools are capable of packing and running an application in an isolated environment that have
the application's dependencies,
required libraries and configuration files for the
application to function properly.

@@

Docker containers are managed by the Docker engine, which is a client-server application, and
is also known as Docker Daemon.

\begin{comment}
consists of the following three main components:

@@

\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
convert english to punjabi
\end{comment}
%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through Command Line Interface (CLI) i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
If a user gets root privileges, it
introduces unthinkable security risks for multi-tenant shared
environments. Due to this reason, Docker is not supported by
HPC environments.

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below.

@@

On the other hand, a Singularity image is a single immutable file and
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.

\begin{comment}
Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

@@

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. 
DockerHub uses gzip compression for
transferring layers.There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch.Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}

@@

On the other hand, a Singularity image is a single immutable file and 
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.
Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.
\end{comment}
\subsection{Application frameworks}

@@

@@

\subsection{Linux Distributions and Vulnerability Databases}
